\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[scale=0.85]{geometry}
\usepackage{multicol}

% Personal info
\name{Ivan}{Egorov}
\title{Senior Software Engineer}
\email{me@egori.ch}
%\homepage{egori.ch}
\social[linkedin]{in/egorich}
\social[github]{egorich239}
\address{Zürich}{Switzerland}

\begin{document}

\makecvtitle

\section{Summary}
Software Engineer with two decades of expertise spanning system runtimes,
developer infrastructure, large-scale data processing, and AI/ML
applications. Proven ability to deliver high-performance, scalable systems
across diverse domains. Strong proficiency in C++, Python, and systems
programming—from bare metal to distributed architectures at scale.

\section{Experience}

\cventry{Aug 2022 -- Mar 2025}{Software Engineer}{Daedalean AI}{Zürich, Switzerland}{}{
Developing autonomous piloting systems for aviation.
\begin{itemize}
    \item Designed and developed OS drivers and image processing applications
    for the PilotEye visual traffic detection system.
    \item Built a prototype for visual obstacle detection system.
    \item Ported an in-house IPC technology runtime to Rust.
\end{itemize}
}

\cventry{Nov 2019 -- Jun 2022}{Software Engineer, Oculus}{Facebook}{Zürich, Switzerland}{}{
Key contributor to Oculus' OS and runtime platform migration.
\begin{itemize}
    \item Led migration to a new non-POSIX OS: implemented `pthread` library,
    ported internal and third-party libraries.
    \item Designed an IDL and C++ codegen system for an in-house IPC framework.
    \item Achieved a multi-fold reduction of binary footprint of Oculus C++ logging library.
\end{itemize}
}

\cventry{Jan 2010 -- Oct 2019}{Software Engineer}{Google}{Zürich, Switzerland}{}{
Contributed to Chrome, Maps, Assistant, and YouTube in SWE and SRE roles.
\begin{itemize}
    \item Optimized Google Maps Transit for early smartphones: backend and
    algorithm tuning, resource forecasting, stability improvements.
    \item Improved latency and cost of a Maps quality evaluation pipeline.
    \item Boosted cache hit rate in YouTube personalization via query stream sharding.
    \item Built and maintained a micro-benchmarking infrastructure for Chrome.
\end{itemize}
}

\cventry{2009 -- 2010}{Software Engineer}{EMC}{St. Petersburg, Russia}{}{
Worked on a performance analysis tool for large-scale storage systems.
Introduced unit testing, migrated team codebase to SVN, contributed various
improvements to the tool.
}

\cventry{2007 -- 2008}{Compiler Intern}{Intel}{St. Petersburg, Russia}{}{
Built VLIW debugger for implementations (in emulator, FPGA, and hardware) of a
custom chip architecture. Researched instruction set compaction.
}

\section{Education}
\cventry{2004 -- 2009}{MSc in Software Engineering}{Saint-Petersburg State University}{St. Petersburg, Russia}{}{}

\section{Skills}
\cvitem{Languages}{C++, C, Rust, Python, Go}
\cvitem{Systems}{Runtime libraries, IPC, logging}
\cvitem{Scale}{Data pipelines, distributed systems, performance optimization}
\cvitem{Spoken}{Russian (native), English (fluent), German (intermediate)}

\end{document}
